---
title: "Problem set 2"
author: "Juntong Lin"
date: "2020/10/19"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, cache=TRUE}
# library
library(tidyverse)
library(here)
```

# Juntong Lin
# 2020/10/19

## Abstract

This study is mainly to explore the relationship between people's feelings of life and their individual income, and look out at which level of income will have a significant impact. I also choose the marital status, house owning or renting, and religion as the other affecting variables on life feelings. A linear model is chosen for this study. As a result, I find out individual income is a signifacnt factor, however, the increase of feelings life is not that obvious in the first four levels of income. 

## Introduction

In recent years, people are having more and more preasures, and it's hard to have a satisfied life. After looking at this dataset, I'm interested in the feelings of life of people, and would like to find out some variables would have significant relation with it. Therefore, in this study, I choose several varibles in common views that will affect the feeligs of life. Since there are different levels in each variable, when coding, I would set a base level for each of them. Also, as my main focus is on individual income, I would study all the levels of income and find out their relationship and significance. After that, I would summary each level of income and code the regression of them. The result of relationship of each variable may be easy to guess, but different levels within each variables would have different significance.

## Data

```{r, cache=TRUE}
# Load Data
GSS <- read_csv(here("gss.csv")) %>%
  subset(select = c(feelings_life, marital_status, own_rent, religion_has_affiliation, income_respondent))

# omit nas
GSS <- GSS %>%
  na.omit()
```
feelings_life, marital_status, own_rent, religion_has_affiliation, and income_respondent are the dat I decided to choose. I chose them because they are some common views of happiness of life. Also, I decided to remove the NAs in the data. There were 471 out of 20602 datas contains NA, so removing them does not change the sample by much.

## Model

I choose the linear model to study my hypothesis. I choose this model because it is the most clear and simlified, since the variables are all substring and have different levels. This will make it easier to set a base model and study each level's significance.

$$Feelings\_life = a + b_1*marital\_status+ b2 *own\_rent + b3*religion\_has\_affiliation +b4*income\_respondent$$

## Results
```{r, cache=TRUE}
# Descriptive Stats
# Feeling life
GSS %>%
  ggplot(aes(feelings_life)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(title= "Figure 1: Distribution of Feeling_life",
       y = "relative frequencies") +
  theme(plot.title = element_text(hjust=0.5))

# Marital Status
GSS %>%
  ggplot(aes(marital_status)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(title= "Table1: Distribution of Marital_status",
       y = "relative frequencies") +
  theme(plot.title = element_text(hjust=0.5))

# Own_rent
GSS %>%
  ggplot(aes(own_rent)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(title= "Table1: Distribution of own_rent",
       y = "relative frequencies") +
  theme(plot.title = element_text(hjust=0.5))

# Religion
GSS %>%
  ggplot(aes(religion_has_affiliation)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(title= "Table1: Distribution of religion_has_affiliation",
       y = "relative frequencies") +
  theme(plot.title = element_text(hjust=0.5))

# Income_respondent
GSS %>%
  ggplot(aes(income_respondent)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) + 
  scale_y_continuous(labels=scales::percent) +
  labs(title= "Table 2: Distribution of income_respondent",
       y = "relative frequencies") +
  theme(plot.title = element_text(hjust=0.5))

```


```{r, cache=TRUE}
# Do the regression
# First, create dummy variables for the regression
regression_data <- GSS %>%
  mutate(# Dummies for Marital Status
         # Single, never married as the base model
         is_married = (marital_status == "Married"),
         is_living_common_law = (marital_status == "Living common-law"),
         is_divorced = (marital_status == "Divorced"),
         is_separated = (marital_status == "Separated"),
         is_widowed = (marital_status == "Widowed"),
         # Dummies for Own Rent
         # Rented, even if no cash rent is paid as the base model
         is_owned = (own_rent == "Owned by you or a member of this household, even if it i..."),
         is_rented_dk = (own_rent == "Don't know"),
         # Dummies for religion_has_affiliation
         # No religious affiliation as the base model
         is_religion = (religion_has_affiliation == "Has religious affiliation"),
         is_religion_dk = (religion_has_affiliation == "Don't know"),
         # Dummies for income_respondent
         # Do not have a base model yet
         is_0_25 = (income_respondent == "Less than $25,000"),
         is_25_49 = (income_respondent == "$25,000 to $49,999"),
         is_50_74 = (income_respondent == "$50,000 to $74,999"),
         is_75_99 = (income_respondent == "$75,000 to $99,999"),
         is_100_124 = (income_respondent == "$100,000 to $ 124,999"),
         is_125 = (income_respondent == "$125,000 and more")) %>%
  subset(select = -c(marital_status, own_rent, religion_has_affiliation, income_respondent))
  
# DO THE REGRESSION
Model_result1 <- regression_data %>%
   # Less than $25,000 as the base model
  subset(select = - is_0_25) %>%
  lm(feelings_life ~ ., data = .)

summary(Model_result1)

# Plot the barplot to show the difference of Feelings_life from Less than $25,000
Model_result1$coefficients %>%
  .[11:15] %>%
  t() %>%
  as_tibble() %>%
  pivot_longer(cols = c(1:5), names_to = "Group", values_to = "Diff") %>%
  # fix the the group order
  mutate(Group = GSS$income_respondent %>%
           unique() %>%
           .[c(1,3,5,6,4)],
         Group = factor(GSS$income_respondent %>%
                          unique() %>%
                          .[c(1,3,5,6,4)],
                        levels = GSS$income_respondent %>%
                          unique() %>%
                          .[c(1,3,5,6,4)])) %>%
  ggplot(aes(Group, Diff)) +
  geom_col() +
  labs(title= "Figure 1: The Regression Coefficients with Less than $25,000 as Base",
       x = "Income",
       y = "Feelings_life Difference from Less than $25,000") +
  theme(plot.title = element_text(hjust=0.5))

# DO THE REGRESSION
# 25-49 as the base model
Model_result2 <- regression_data %>%
  subset(select = - is_25_49) %>%
  lm(feelings_life ~ ., data = .)

summary(Model_result2)

# 50-74 as the base model
Model_result3 <- regression_data %>%
  subset(select = - is_50_74) %>%
  lm(feelings_life ~ ., data = .)

summary(Model_result3)

# 75-99 as the base model
Model_result4 <- regression_data %>%
  subset(select = - is_75_99) %>%
  lm(feelings_life ~ ., data = .)

summary(Model_result4)

# 100-124 as the base model
Model_result5 <- regression_data %>%
  subset(select = - is_100_124) %>%
  lm(feelings_life ~ ., data = .)

summary(Model_result5)

# above 125 as the base model
Model_result6 <- regression_data %>%
  subset(select = - is_125) %>%
  lm(feelings_life ~ ., data = .)

summary(Model_result6)
```

For the marital statue, when setting is_single as base, the other levels except is_divorcedTRUE are significant. is_ownedTRUE is significant and is_religionTRUE are significant in each level. All the levels of income are significant when setting the below 25 as base level. But when looking into each of them, only the last level is_125TRUE will cause a large change. The bar plot also shows that the feelings life increase slowly and has flutuation in the first four level, only the last level has obvious change.

## Discussion

In conclusion, the marital statue, house owning or renting, religion and income are all significant factors that will affect the feelings of life. For marital statues, getting married and living together do have a more satisfied life than singles, while divorced and seperate has a less satified life than single. Interestingly, widowed seems more satified, and the divorced in not significant. For own_rent, people owning a house will be more satified than those without living place, while renting is unsignificance. For religion, having a belief will be more satisfied than those without belief. And for income, all the level showed its significance, the feeling of life seems to increase as the income level increase. However, when looking into each level precisely, we find out that each levle show significance compared to below 25 level, and the above 125 level show significance to each level below. However, for the middle four levels between the highest and lowest, the increase is not that significant, even it appears fluctuation. The plot also shows a similiar result, such that the lowest level is obvious low and the highest level is obvious high, while the middle of them increase slowly. 

# Weaknesses

The linear model itself may be not precise enough. Though the study of life feeling and income is fine, but other factors are difficult to judge.

# Next Steps

For the next step, I may learn some interesting finding in this study, such as the is_widowedTRUE level in marital variable. Also, I would continue to study if there is a better statistic model for the data. 

## References

[1] Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43),
  1686, https://doi.org/10.21105/joss.01686
  
[2]  Kirill Müller (2017). here: A Simpler Way to Find Your Files. R package version 0.1.
  https://CRAN.R-project.org/package=here
  
[3] gss csv

